Method to infer relatedness using low coverage ancient DNA

### 2021-12-22 paper_overleaf/main.tex
Updates from Overleaf

>>>>

- Variances are proportional to mean

- READ with Chagyrskaya

\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/fil0_read_plot.png}
    \caption{Application of READ on Neandertal specimens from Chagyrskaya. Color of a square represents the relatedness, while the number denotes loglikelihood ratio.}
    \label{figS2}
\end{figure}

- lcMLKIn and kin ibd
\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/lcPlot.png}
    \caption{Application of lcMLkin on Neandertal specimens from Chagyrskaya.}
    \label{figS3}
\end{figure}

-2nd degree with 10M windows
\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/degree2_10Mwin.png}
    \caption{2deg}
    \label{figS4}
\end{figure}

-ROH high diff
